Morality, politics, and cooperation

### 2022-10-05 manuscript/manuscript.Rmd
update 2022-10-05 07:56:44

```{r setup, include=FALSE}
# We recommend that you prepare your raw data for analysis in 'prepare_data.R',
# and end that file with either open_data(yourdata), or closed_data(yourdata).
# Then, uncomment the line below to load the original or synthetic data
# (whichever is available), to allow anyone to reproduce your code:
library("worcs")
run_everything = FALSE
knitr::opts_chunk$set(echo = FALSE, results = "hide", message = FALSE, warning = FALSE)
options(knitr.kable.NA = '')
library(ggplot2)
library(tidySEM)
library(lavaan)
library(semTools)
library(kableExtra)
library(bookdown)
library(psych)
library(knitr)
dat <- load_data(to_envir = FALSE)[1:3]
source("../scales_list.R")
scales_list <- lapply(scales_list, function(i){
  tmp <- lapply(names(i), function(j){ paste0(j, "_", 1:length(i[[j]]))})
  names(tmp) <- names(i)
  tmp
  })
```

@@

res_list <- lapply(mods_cor, function(x){estimate_lavaan(x)})
res_list17 <- res_list
res <- lapply(names(res_list), function(country){
  thisfit = res_list[[country]]
  tab <- bain:::lav_get_estimates(thisfit, standardize = TRUE, retain_which = "~~")
  keep_these <- which(!grepl("~~(secs|sepa)_(soc|eco)$", names(tab$estimate)) & grepl("(secs|sepa)_(soc|eco)~~", names(tab$estimate)))
  estimates <- tab$estimate[keep_these]
  Sigma <- tab$Sigma[[1]][keep_these, keep_these]
  names(estimates) <- paste0(gsub("~~", "_", names(estimates), fixed = TRUE), "_", country)
  names(estimates) <- gsub("^(sepa|secs)_(.+?)_(.+?)_(.+)$", "\\3_\\1_\\2_\\4", names(estimates))
  colnames(Sigma) <- rownames(Sigma) <- names(estimates)
  list(est = estimates, sig = Sigma)
})
names(res) <- names(res_list)
res_h17 <- res
# Get individual BFs for each sample
bf_individual <- sapply(1:length(res_list), function(i){
  hyp <- paste2(unlist(
    lapply(
      lapply(hypotheses[1:7], removeothercountries, cnt = names(res_list)[i]),
      removeparameters, est = res[[i]]$est)
    ), collapse = "; ")
  tmp <- BF(x = res[[i]]$est,
            hypothesis = hyp,
            Sigma = res[[i]]$sig,
            n = sample_sizes[i])
  tmp$BFtu_confirmatory[1:7]
})
out_cors <- apply(bf_individual, 1, prod)

@@

```{r, eval = run_everything}
library(worcs)
library(lavaan)
library(BFpack)
library(ggplot2)
library(tidySEM)
tris <- load_data(to_envir = FALSE)[["tris"]]

@@

res17 <- estimate_lavaan(mod_cor)
res_tris <- res17
tab <-
  bain:::lav_get_estimates(res17, standardize = TRUE, retain_which = "~~")
keep_these <-
  which(
    !grepl("~~(secs|sepa)_(soc|eco)$", names(tab$estimate)) &
      grepl("(secs|sepa)_(soc|eco)~~", names(tab$estimate))
  )
estimates <- tab$estimate[keep_these]
Sigma <- tab$Sigma[[1]][keep_these, keep_these]
names(estimates) <-
  gsub("~~", "_", names(estimates), fixed = TRUE)
names(estimates) <-
  gsub("^(sepa|secs)_(.+?)_(.+?)$", "\\3_\\1_\\2", names(estimates))
colnames(Sigma) <- rownames(Sigma) <- names(estimates)
res <- list(est = estimates, sig = Sigma)
res17 <- res
# Get BF
hyp <- paste2(unlist(lapply(
  gsub("_us", "", lapply(hypotheses[1:7], removeothercountries, cnt = "us")),
  removeparameters, est = res$est
)), collapse = "; ")
tmp <- BF(
  x = res$est,
  hypothesis = hyp,
  Sigma = res$sig,
  n = sample_sizes
)

>>>>

```{r setup, include=FALSE}
# We recommend that you prepare your raw data for analysis in 'prepare_data.R',
# and end that file with either open_data(yourdata), or closed_data(yourdata).
# Then, uncomment the line below to load the original or synthetic data
# (whichever is available), to allow anyone to reproduce your code:
library("worcs")
run_everything = TRUE
knitr::opts_chunk$set(echo = FALSE, results = "hide", message = FALSE, warning = FALSE)
options(knitr.kable.NA = '')
library(ggplot2)
library(tidySEM)
library(lavaan)
library(semTools)
library(kableExtra)
library(bookdown)
library(psych)
library(knitr)
dat <- load_data(to_envir = FALSE)[1:3]
source("../scales_list.R")
scales_list <- lapply(scales_list, function(i){
  tmp <- lapply(names(i), function(j){ paste0(j, "_", 1:length(i[[j]]))})
  names(tmp) <- names(i)
  tmp
  })
```

@@

res_list <- lapply(mods_cor, function(x){estimate_lavaan(x)})
# simdat <- lapply(1:3, function(i) simulateData(parTable(res_list[[i]]), sample.nobs = sample_sizes[i]))
# for(i in 1:3){
#   worcs::add_synthetic(simdat[[i]], original_name = paste0(names(mods_cor)[i], ".csv"), worcs_directory = "../")
# }
res_list17 <- res_list
res <- lapply(names(res_list), function(country){
  thisfit = res_list[[country]]
  tab <- bain:::lav_get_estimates(thisfit, standardize = TRUE, retain_which = "~~")
  keep_these <- which(!grepl("~~(secs|sepa)_(soc|eco)$", names(tab$estimate)) & grepl("(secs|sepa)_(soc|eco)~~", names(tab$estimate)))
  estimates <- tab$estimate[keep_these]
  Sigma <- tab$Sigma[[1]][keep_these, keep_these]
  names(estimates) <- paste0(gsub("~~", "_", names(estimates), fixed = TRUE), "_", country)
  names(estimates) <- gsub("^(sepa|secs)_(.+?)_(.+?)_(.+)$", "\\3_\\1_\\2_\\4", names(estimates))
  colnames(Sigma) <- rownames(Sigma) <- names(estimates)
  list(est = estimates, sig = Sigma)
})
names(res) <- names(res_list)
res_h17 <- res
# Get individual BFs for each sample
bf_individual <- sapply(1:length(res_list), function(i){
  hyp <- paste2(unlist(
    lapply(
      lapply(hypotheses[1:7], removeothercountries, cnt = names(res_list)[i]),
      removeparameters, est = res[[i]]$est)
    ), collapse = "; ")
  tmp <- BF(x = res[[i]]$est,
            hypothesis = hyp,
            Sigma = res[[i]]$sig,
            n = sample_sizes[i])
  tmp$BFtu_confirmatory[1:7]
})
out_cors <- apply(bf_individual, 1, prod)

@@

```{r, eval = run_everything}
library(worcs)
library(lavaan)
library(BFpack)
library(ggplot2)
library(tidySEM)
tris <- load_data(to_envir = FALSE, worcs_directory = "../")[["tris"]]

@@

res17 <- estimate_lavaan(mod_cor)
#simdat <- simulateData(parTable(res17), sample.nobs = nrow(tris))
#worcs::add_synthetic(simdat, original_name = "tris.csv", worcs_directory = "../")

res_tris <- res17
tab <-
  bain:::lav_get_estimates(res17, standardize = TRUE, retain_which = "~~")
keep_these <-
  which(
    !grepl("~~(secs|sepa)_(soc|eco)$", names(tab$estimate)) &
      grepl("(secs|sepa)_(soc|eco)~~", names(tab$estimate))
  )
estimates <- tab$estimate[keep_these]
Sigma <- tab$Sigma[[1]][keep_these, keep_these]
names(estimates) <-
  gsub("~~", "_", names(estimates), fixed = TRUE)
names(estimates) <-
  gsub("^(sepa|secs)_(.+?)_(.+?)$", "\\3_\\1_\\2", names(estimates))
colnames(Sigma) <- rownames(Sigma) <- names(estimates)
res <- list(est = estimates, sig = Sigma)
res17 <- res
# Get BF
hyp <- paste2(unlist(lapply(
  gsub("_us", "", lapply(hypotheses[1:7], removeothercountries, cnt = "us")),
  removeparameters, est = res$est
)), collapse = "; ")
tmp <- BF(
  x = res$est,
  hypothesis = hyp,
  Sigma = res$sig,
  n = sample_sizes
)
